---
title: "imdb process fields"
output: html_notebook
---

```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(readr)
library(tidyr)
```

Reading the separated data file:

```{r}
imdb_sep <- read_tsv("../data/imdb_data_separated.txt", col_names = FALSE, col_types = list(col_character(), col_character(), col_character(), col_character()))
names(imdb_sep) <- c("IMDB_ID", "field_type", "field_id", "field_name")
imdb_sep
```



```{r}
imdb_sep$field_type %>% unique()
```

Num_roles\tName\tCast_id\tMovie_id_list\n
credits-by-name.txt
```{r, eval=FALSE}
imdb_sep %>% 
  filter(field_type == "cast") %>% 
  group_by(field_id, field_name) %>% 
  summarise(num_roles = n(), movie_ids = paste(IMDB_ID %>% unique(), collapse = ", ")) %>% 
  ungroup() %>% 
  select(cast_id = field_id, cast_name = field_name, num_roles, movie_ids) %>% 
  write_tsv("../data/intermediate/imdb-credits-by-name.tsv", col_names = TRUE)
```

Reading tsv

```{r, echo=FALSE}
imdb_tsv <- read_tsv("../data/imdb.tsv")
imdb_tsv
```

# For each actor, compute the number of times
# they appeared in a movie with each genre (by adding up
# the movie_genres[] rows for each movie they are listed
# as appearing in).
# Third pass: For each movie, accumulate the individual
# actor-genre affinity scores for every actor credited
# as appearing in that movie (provided that the
# actor-genre affinity score exceeds the threshold)

```{r}
duplicate_cast <- imdb_sep %>% 
  filter(field_type == "cast") %>% 
  select(field_id, field_name) %>% 
  unique() %>% 
  group_by(field_id) %>% 
  summarise(count = n()) %>% 
  ungroup() %>% 
  filter(count == 2) %>% 
  .$field_id

imdb_cast_movie_genre <- imdb_tsv %>% 
  select(IMDB_ID, `Sci-Fi`:Biography) %>% 
  right_join(imdb_sep %>% filter(field_type == "cast", !field_id %in% duplicate_cast)) 

imdb_actor_genre_affinity <- imdb_cast_movie_genre %>% 
  select(`Sci-Fi`:Biography, field_id, field_name) %>% 
  gather(genre, genre_score, `Sci-Fi`:Biography) %>% 
  group_by(field_name, field_id, genre) %>% 
  summarise(genre_affinity = sum(genre_score)) %>% 
  ungroup() %>% 
  filter(genre_affinity > 10) %>% 
  spread(genre, genre_affinity)

imdb_actor_genre_affinity
```

Lets create movie genre affinity score

```{r}
movie_genre_affinity_score <- imdb_sep %>% 
  filter(field_type == "cast") %>% 
  inner_join(imdb_actor_genre_affinity) %>% 
  select(IMDB_ID, Action:Western) %>% 
  group_by(IMDB_ID) %>% 
  summarise_all(.funs = funs("sum")) 

movie_genre_affinity_score[is.na(movie_genre_affinity_score)] <- 0

movie_genre_affinity_score %>% 
  write_tsv("../data/imdb-movie-cast-scores.tsv")
```

------------------

We can now create affinity scores for all fields:

```{r}
fields <- c("directors", "production_companies", "cast", "writer", "producer", "composer", "miscellaneous_crew", "distributors", "editor", "cinematographer", "production_designer")

for (f in fields) {
  print(f)
  duplicate_directors <- imdb_sep %>% 
  filter(field_type == f) %>% 
  select(field_id, field_name) %>% 
  unique() %>% 
  group_by(field_id) %>% 
  summarise(count = n()) %>% 
  ungroup() %>% 
  filter(count == 2) %>% 
  .$field_id

  imdb_directors_movie_genre <- imdb_tsv %>% 
  select(IMDB_ID, `Sci-Fi`:Biography) %>% 
  right_join(imdb_sep %>% filter(field_type == f, !field_id %in% duplicate_directors)) 

  imdb_directors_genre_affinity <- imdb_directors_movie_genre %>% 
  select(`Sci-Fi`:Biography, field_id, field_name) %>% 
  gather(genre, genre_score, `Sci-Fi`:Biography) %>% 
  group_by(field_name, field_id, genre) %>% 
  summarise(genre_affinity = sum(genre_score)) %>% 
  ungroup() %>% 
  filter(genre_affinity > 10) %>% 
  spread(genre, genre_affinity)
  
  movie_genre_affinity_score <- imdb_sep %>% 
  filter(field_type == f) %>% 
  inner_join(imdb_directors_genre_affinity) %>% 
  select(IMDB_ID, Action:War) %>% 
  group_by(IMDB_ID) %>% 
  summarise_all(.funs = funs("sum")) 

  movie_genre_affinity_score[is.na(movie_genre_affinity_score)] <- 0

  movie_genre_affinity_score %>% 
  write_tsv(paste0("../data/imdb-movie-", f, "-scores.tsv"))
  print(f)
}
```

